---
title: "viz_part_02"
output: github_document
date: "2022-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Let's import data

```{r}
library(tidyverse)
library(ggridges)
```

This code from course website.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


## Scatterplot 

But better this time

```{r}
weather_df %>% 
  ggplot(aes( x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    x = "Minimun Daily Temp (C)" ,
    y = "Maximum Daily Temp (C)" , 
    title = "Scatterplot of daily temp extremes" ,
    caption = "Data come from the rnoaa package"
  ) +
  scale_x_continuous(
    breaks = c(10, 0,15),
    labels = c("-10C", "0C", "15C")
  ) 
```

make a new version


```{r}
weather_df %>% 
  ggplot(aes( x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    x = "Minimun Daily Temp (C)" ,
    y = "Maximum Daily Temp (C)" , 
    title = "Scatterplot of daily temp extremes" ,
    caption = "Data come from the rnoaa package"
  ) +
  scale_color_hue(
    name = "Location",
    h = c(100,300))
```
`scale_color_hue()` not recommended 

```{r}
weather_df %>% 
  ggplot(aes( x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    x = "Minimun Daily Temp (C)" ,
    y = "Maximum Daily Temp (C)" , 
    title = "Scatterplot of daily temp extremes" ,
    caption = "Data come from the rnoaa package"
  ) +
  viridis::scale_color_viridis( 
    name = "Location",
    discrete = TRUE
  )
```


## Themes
```{r}
ggp_weather =
  weather_df %>% 
  ggplot(aes( x = tmin, y = tmax, color = name)) +
  geom_point(alpha = .5) +
  labs(
    x = "Minimun Daily Temp (C)" ,
    y = "Maximum Daily Temp (C)" , 
    title = "Scatterplot of daily temp extremes" ,
    caption = "Data come from the rnoaa package"
  ) +
  viridis::scale_color_viridis( 
    name = "Location",
    discrete = TRUE)
```

```{r}
ggp_weather +
  theme_minimal()
  theme(legend.position = "bottom")
```

* Order matters 
`theme_minimal()` wiil change the whole plot, usually put at the frount of the `theme` statement.
`theme(legend.position = "bottom")` will change the position of legend, usually put at the end of the `theme` statement.
If `theme_minimal()`put behind the `theme(legend.position = "bottom")`, the plot will be regraph. 



