---
title: "viz_part_01"
output: github_document
date: "2022-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Let's import data

```{r}
library(tidyverse)
library(ggridges)
```

This code from course website.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's make a scatterplot

```{r}
ggplot(weather_df,aes(x = tmin, y = tmax)) + geom_point()
```

Let's make the same scaterplot, but different
```{r}
weather_df %>% 
  drop_na() %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) + geom_point()
```

Let's keep make the same scaterplot, but different

```{r}
weather_scatterplot = 
  weather_df %>% 
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_scatterplot +
  geom_point()
```


## Let's fancy this up a bit

```{r}
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.3) +
  geom_smooth( se = FALSE)
```

similar thing 

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name)) +
  geom_smooth()
```


Maybe make separate panels.
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.3) +
  geom_smooth( se = FALSE) +
  facet_grid(. ~ name)
```
`  facet_grid(. ~ name)` define column and rows

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.3) +
  geom_smooth( se = FALSE) +
  facet_grid(name ~ .)
```


`t max` and `t min` is boring, let's spice it up same.

```{r}
weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth (se = FALSE) +
  facet_grid(. ~ name) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
``` 


## Some quick stuff

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32) %>% 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE)
```


```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```


## Univariate plots ...

histograms, barplot, boxplot, violins, ...

```{r}
weather_df %>% 
  ggplot(aes (x = tmax, fill = name)) +
  geom_histogram() + 
  facet_grid(. ~ name)
```

Let;s see more options

```{r}
weather_df %>% 
  ggplot(aes (x = tmax, fill = name)) +
  geom_density( alpha = .3) 
```

boxplot?

```{r}
weather_df %>% 
  ggplot(aes (x = name, y = tmax, fill = name )) +
  geom_boxplot() 
```


violin? 

```{r}
weather_df %>% 
  ggplot(aes (x = name, y = tmax, fill = name )) +
  geom_violin() 
```

or 
```{r}
weather_df %>%
  ggplot(aes(x = tmax, y = name))+
  geom_density_ridges()
```


## saving and embedding plots

first -- let's save a plot.

```{r}
weather_scatterplot = 
  weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = .3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
weather_scatterplot

ggsave("results/weather_scatterplot.pdf", weather_scatterplot,
       width = 8, height = 5)

ggsave(
  file = "results/weather_scatterplot.pdf", 
  plot = weather_scatterplot,
  width = 8, height = 5)
```

embedding

```{r}
weather_scatterplot
```

```{r, fig.width=12, fig.height=6 }
weather_scatterplot
```

```{r, fig.width=6, fig.height=3 }
weather_scatterplot
```

